---
title: "An Example R Markdown Document"
author: "Titus Brown, modified from Andrew Marder"
date: "12/15/2016"
output: html_document
---

R Markdown is really cool! It allows one to combine text and code smoothly, which lets you convey the full analysis together with a discussion all in one document (you know, like a paper for publication, but better).

Text is written using Markdown syntax, and code is placed inside code chunks. In RStudio, clicking the **Knit** button will generate a document that knits together the text, code, and output from executing the code chunks. Let's jump into why R Markdown is so great.

To start, let's load the gapminder data set using `read.csv()`.

```{r}
library(tidyverse)
gapminder <- read.csv('../data/gapminder-FiveYearData.csv')
```

Now that we've loaded the data, let's take a quick look at it:

```{r}
head(gapminder)
```

...and embed one of our pretty graphs:

```{r}
ggplot(gapminder, aes(x = gdpPercap, y = lifeExp)) +
    geom_point(aes(color = continent)) + 
    scale_x_log10() +
    geom_smooth(method = 'lm') +
    theme_bw()
```

How cool is that!? Rendering this R Markdown document creates an image file of the graph above and embeds that image file in the final HTML document.

The default behavior of R Markdown is to "echo" each code chunk in the resulting document. The easiest way to remove code from the final document is the set the `echo` option to `FALSE`.

```{r, echo = FALSE}
ggplot(gapminder, aes(x = gdpPercap, y = lifeExp)) +
    geom_point(aes(color = continent)) + 
    scale_x_log10() +
    geom_smooth(method = 'lm') +
    theme_bw()
```

An exercise to try for yourself, assuming you can get everything running:

pick your favorite plot from [the gapminder lesson](http://data-lessons.github.io/gapminder-R/04-ggplot.html) and modify the final plot (just above) in the RMarkdown file to make that plot instead of this one.  